### 2019-11-21 l2_mpi_sample.tex
Fiddle with code, tables.

  std::vector<MPI_Request> requests;
  for (long row = 0; row < g.height; ++row) {
    if (g.contains_point(row, rank)) {
      long idx = 0;
      requests.clear();

      for (long dep : g.deps(row, rank)) {
        MPI_Request req;
        MPI_Irecv(inputs[idx], g.output_bytes, MPI_BYTE,
          dep, 0, MPI_COMM_WORLD, &req);
        requests.push_back(req); idx++;
      }

      for (long dep : g.reverse_deps(row, rank)) {
        MPI_Request req;
        MPI_Isend(output, g.output_bytes, MPI_BYTE,
          dep, 0, MPI_COMM_WORLD, &req);
        requests.push_back(req);
      }

@@

      g.execute_point(row, rank, output, g.output_bytes_per_task,
        inputs, input_bytes, idx,
        scratch, g.scratch_bytes_per_task);
    }
  }
}
\end{lstlisting}

>>>>

  std::vector<MPI_Request> requests;
  for (long t = 0; t < g.height; ++t) {
    if (g.contains_point(t, rank)) {
      long idx = 0;
      requests.clear();

      for (long dep : g.deps(t, rank)) {
        MPI_Request req;
        MPI_Irecv(inputs[idx], g.output_bytes, MPI_BYTE,
          dep, 0, MPI_COMM_WORLD, &req);
        requests.push_back(req);
        idx++;
      }

      for (long dep : g.reverse_deps(t, rank)) {
        MPI_Request req;
        MPI_Isend(output, g.output_bytes, MPI_BYTE,
          dep, 0, MPI_COMM_WORLD, &req);
        requests.push_back(req);
      }

@@

      g.execute_point(t, rank, output, g.output_bytes_per_task,
        inputs, input_bytes, idx,
        scratch, g.scratch_bytes_per_task);
    }
  }
}
\end{lstlisting}
